### 2024-02-19 author-kit-CVPR2024-v2/sec/1_intro.tex
Update 1_intro.tex

Another example is a DancePal Hackathon project, which adopts a more technical approach by 
comparing an ideal video with the end user's video skeletons. This method involves analyzing the 
skeletal poses extracted from both videos and identifying discrepancies between them. While this 
approach has the potential to provide personalized feedback to users based on their own performances, 
it comes with several challenges. Firstly, it requires an ideal video with specific lighting, 
background, and perspective conditions to serve as a reference, which may not always be feasible 
to obtain. Additionally, accurately mapping movements onto predefined definitions can be difficult, 
especially for complex dance sequences with varying styles and interpretations. As a result, the 
effectiveness of this approach may be limited by the availability of suitable reference videos and 
the accuracy of the mapping process.

@@

\subsection{Useful Techniques}
Several computer vision techniques offer promising avenues for addressing the challenge of learning 
dance from online videos by providing deeper insights into the dynamics and nuances of dance 
movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of movements, including depth information. This 
 allows for a more accurate and detailed representation of the dancer's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 dance choreographies.

@@

Trajectory analysis techniques can track the trajectories of specific body parts or movements 
over time, allowing for the analysis of movement patterns, velocities, and accelerations. This 
can provide valuable insights into the rhythmic and dynamic aspects of dance performances, 
helping learners to better understand the timing and pacing of movements. Video segmentation and 
tracking methods can segment dance videos into individual sequences or movements, allowing for more 
focused analysis and comparison of specific choreographic elements.

>>>>

Another example is a DancePal Hackathon project, which adopts a more technical approach by 
comparing an ideal video with the end user's video skeletons. \cite{Authors14c} This method involves analyzing the 
skeletal poses extracted from both videos and identifying discrepancies between them. While this 
approach has the potential to provide personalized feedback to users based on their own performances, 
it comes with several challenges. Firstly, it requires an ideal video with specific lighting, 
background, and perspective conditions to serve as a reference, which may not always be feasible 
to obtain. Additionally, accurately mapping movements onto predefined definitions can be difficult, 
especially for complex dance sequences with varying styles and interpretations. As a result, the 
effectiveness of this approach may be limited by the availability of suitable reference videos and 
the accuracy of the mapping process.

@@

\subsection{Useful Techniques}
Several computer vision techniques offer promising avenues for addressing the challenge of learning 
dance from online videos by providing deeper insights into the dynamics and nuances of dance 
movements. One such technique involves exploring 3D models instead of traditional 2D skeletonization
 methods to create more comprehensive representations of dance movements. Unlike 2D skeletonization, 
 which captures only the spatial coordinates of key body joints in a single plane, 3D modeling 
 techniques can capture the full spatial extent of movements, including depth information. \cite{Alpher03}This 
 allows for a more accurate and detailed representation of the dancer's body and movements in 
 three-dimensional space, which is particularly valuable for capturing complex and multi-dimensional 
 dance choreographies.

@@

Trajectory analysis techniques can track the trajectories of specific body parts or movements 
over time, allowing for the analysis of movement patterns, velocities, and accelerations. \cite{Alpher02}This 
can provide valuable insights into the rhythmic and dynamic aspects of dance performances, 
helping learners to better understand the timing and pacing of movements. Video segmentation and 
tracking methods can segment dance videos into individual sequences or movements, allowing for more 
focused analysis and comparison of specific choreographic elements.
